%!TEX root = ../template.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% chapter4.tex
%% NOVA thesis document file
%%
%% Chapter with lots of dummy text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\typeout{NT FILE chapter4.tex}

\chapter*{Glossary}
\addcontentsline{toc}{chapter}{Glossary}

\label{cha:glossary}

% ACABAR/ALTERAR

On the course of this paper, there will be many words/expressions that are mainly used in therms of programming. In order to help the reader, here are the most common words that will appear in the paper and its definitions.

\section*{IDE} 
\label{sub:ide}

An integrated development environment (IDE) is a software application that provides the necessary means for software development. It normally consists of a source code editor, build automation tools, and a debugger.
For the development of the software code, the used IDE was PyCharm and for the development of the GUI it was used the Visual Studio Code.

\section*{GUI} 
\label{sub:gui}

A Graphical User Interface (GUI) is the first thing the user sees and interacts with when opening an application or website. It allows the user to interact with the application through the help of buttons, graphics, and such instead of the need for coding.
Depending on how it is designed, it might enhance the users experience with the application or worsen it, therefore its importance.

\section*{Module} 
\label{sub:module}

Modules are files containing specific python functions, definitions, and statements that can be called into the main program without the need of rewriting its code, making it easier and more convenient for programmers to code.

\newpage

\section*{Library} 
\label{sub:library}

% https://docs.python.org/2/tutorial/modules.html
% https://docs.python.org/2/library/

% Python Libraries are a set of useful functions that eliminate the need for writing codes from scratch. There are over 137,000 python libraries present today. Python libraries play a vital role in developing machine learning, data science, data visualization, image and data manipulation applications, and more.
% A Python library is a collection of related modules. It contains bundles of code that can be used repeatedly in different programs. It makes Python Programming simpler and convenient for the programmer

A Library is, in a simple manner of speech, a collection of related modules.
Some of the most known libraries, that will be discussed during this paper, are, i.e., Tkinter (Standard GUI library for Python); MatPlotLib (Useful for its visual characteristics). 


%\section*{Framework} 
%\label{sub:framework}

%A framework is a 


%In computer programming, a software framework is an abstraction in which software, providing generic functionality, can be selectively changed by additional user-written code, thus providing application-specific software. It provides a standard way to build and deploy applications and is a universal, reusable software environment that provides particular functionality as part of a larger software platform to facilitate the development of software applications, products and solutions. Software frameworks may include support programs, compilers, code libraries, toolsets, and application programming interfaces (APIs) that bring together all the different components to enable development of a project or system.


% https://hackr.io/blog/what-is-frameworks

\section*{Cross-Platform Framework} 
\label{sub:cp_framework}

%Passar para palavras próprias?

A cross-platform app development framework is a set of tools that allows the user to use a single codebase to build native or native-like apps for multiple platforms such as Android, iOS, Desktop and Web.

\section*{Open Source }
\label{sub:open_source}

Open Source, originaly Open Source Software (OSS), is the therm used for codes that are meant to be publicly accessible. In other words, open source codes are codes which anyone can see, modify, and distribute as they please. %(PLEASE???)


\section*{API}
\label{sub:api}

API stands for \textbf{A'}pplication \textbf{P}rogramming \textbf{I}nterface, which is a set of definitions and protocols for building and integrating application software

%PASSAR POR PALAVRAS PRÓPRIAS

\section*{OS}
\label{os}

OS stands for \textbf{O}perating \textbf{S}ystem.