%!TEX root = ../template.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% glossary.tex
%% NOVA thesis document file
%%
%% Glossary definition
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\typeout{NT FILE glossary.tex}

\newglossaryentry{computer}{
	name={computer}, 
	description={An electronic device which is capable of receiving information (data) in a particular form and of performing a sequence of operations in accordance with a predetermined but variable set of procedural instructions (program) to produce a result in the form of information or signals. This is a test that adds a citation~\cite{Artho04} to the glossary!}
}


\newglossaryentry{ide}{
	name={ide}, 
	description={An integrated development environment (IDE) is a software application that provides the necessary means for software development. It normally consists of a source code editor, build automation tools, and a debugger.
For the development of the NAME OF SOFTWARE CREATED, the used IDE was the Spyder (as well as for the development of the GUI//and for the development of the GUI it was used the XXXX).}
}


\newglossaryentry{GUI}{
	name={GUI}, 
	description={A Graphical User Interface (GUI) is the first thing the user sees and interacts with when opening an application or website. It allows the user to interact with the application through the help of buttons, graphics, and such instead of the need for coding.
Depending on how it is designed, it might enhance the users experience with the application or worsen it, therefore/ence its importance.}
}


\newglossaryentry{Library}{
	name={Library}, 
	description={A Library is, in a simple manner of speech, a collection of related modules.
Modules, on the other hand, are files containing specific python functions, definitions, and statements that can be called into/upon the main program without the need of rewriting its code, making it easier and more convenient for programmers to code.
Some of the most known libraries that will be discussed during this paper are, i.e., Tkinter (Standard GUI library for Python); MatPlotLib (Useful for its visual characteristics).}
}


% https://docs.python.org/2/tutorial/modules.html
% https://docs.python.org/2/library/

% Python Libraries are a set of useful functions that eliminate the need for writing codes from scratch. There are over 137,000 python libraries present today. Python libraries play a vital role in developing machine learning, data science, data visualization, image and data manipulation applications, and more.
% A Python library is a collection of related modules. It contains bundles of code that can be used repeatedly in different programs. It makes Python Programming simpler and convenient for the programmer


\newglossaryentry{Cross-Platform Framework}{
	name={Cross-Platform Framework}, 
	description={A cross-platform app development framework is a set of tools that allows you to use a single codebase to build native or native-like apps for multiple platforms such as Android, iOS, Desktop and Web.}
}
%Passar para palavras próprias!!!!!!!!!


\newglossaryentry{Open Source}{
	name={Open Source}, 
	description={
Open Source, originaly Open Source Software (OSS), is the therm used for codes that are meant to be publicly accessible. In other words, open source codes are codes which anyone can see, modify and distribute as they please.} %(PLEASE???)
}


\newglossaryentry{Copyright License}{
	name={Copyright License}, 
	description={
Open Source, originaly Open Source Software (OSS), is the therm used for codes that are meant to be publicly accessible. In other words, open source codes are codes which anyone can see, modify and distribute as they please.} %(PLEASE???)
}
